\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage[empty]{fullpage}
\usepackage{geometry}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage[most]{tcolorbox}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{verbatim}
\usepackage{lipsum}
\usepackage{marvosym}
\usepackage{cfr-lm}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage{lastpage}

\definecolor{darkblue}{RGB}{0,0,139}

\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

\geometry{
  left=1.4cm,
  right=1.2cm,
  top=0.8cm,
  bottom=1cm
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{14pt}
\newcommand{\PageNumFont}{\small}
\fancyfoot[C]{\raisebox{0pt}[\height][\depth]{\PageNumFont - \arabic{page}\ -}}

\setlength{\multicolsep}{0pt}
\raggedright
\setlength{\tabcolsep}{0in}
\urlstyle{same}

\titleformat{\section}{
  \scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule]
\titlespacing*{\section}{0pt}{8pt}{6pt}

\setlist[itemize]{leftmargin=*, labelsep=1mm, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0.6mm}
\setlist[enumerate]{leftmargin=*, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=0.6mm}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\tcbset{
    frame code={},
    center title,
    left=0pt, right=0pt, top=0pt, bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt, outer arc=0pt,
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}

\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

\newcommand{\headerfonti}{\fontfamily{phv}\selectfont}
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont}
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont}
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont}
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont}
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont}
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont}
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont}
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont}
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont}

\newcommand{\resumeItem}[2]{%
  \item{\textbf{#1}\hspace{0.5mm}#2}%
}

\newcommand{\resumePOR}[3]{%
\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}}
    \end{tabular*}
}

\newcommand{\resumeSubheading}[4]{%
\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} & \footnotesize{#2}\\
    \end{tabular*}
}

\newcommand{\resumeProject}[4]{%
\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}
\headerfontiii

\noindent
{\Huge\textbf{Hyeongjin Kim}}\\[1.2mm]
\small{
Incheon, Republic of Korea \,|\, +82 10 3187 9925 \,|\, \href{mailto:ky942400@gmail.com}{ky942400@gmail.com} \\
\socialicon{\faGithub} \href{https://github.com/EliseEgkart}{GitHub: EliseEgkart} \,|\, \socialicon{\faYoutube} \href{https://www.youtube.com/@Hyeongjin-kim}{YouTube: @Hyeongjin-kim} \,|\, \socialicon{\faGlobe} \href{https://eliseegkart.github.io/portfolio_Hyeongjin_Kim/}{Web Portfolio}
}
\vspace*{3mm}

\section{\textbf{Profile}}
\small{
Undergraduate student in Embedded Systems Engineering with practical experience in robotics, autonomous driving, and embedded systems.
Skilled in ROS 2-based robotic system development, sensor fusion, communication system design, and embedded firmware implementation.
}

\section{\textbf{Research Interests}}
\small{
Reinforcement learning for intelligent robotic systems, Multi-agent distributed systems and large-scale infrastructure optimization, multi-modal 3D perception, V2X-enabled networked systems, UAV-assisted intelligent transportation systems.
}

\section{\textbf{Education}}
\resumeSubHeadingListStart

  \resumeSubheading
  {Hanyang University}{Seoul, Republic of Korea}
  {M.S. in Electrical Engineering (Incoming)}{Starting Sep. 2026}

  \vspace{0.5em}

  \resumeSubheading
  {Incheon National University}{Incheon, Republic of Korea}
  {B.S. in Embedded Systems Engineering}{Mar. 2021.03 -- 2026.08}
  \resumeItemListStart
    \item GPA: 4.28 / 4.5 \hfill (140 / 140 credits completed)
  \resumeItemListEnd

\resumeSubHeadingListEnd

\section{\textbf{Research and Professional Experience}}
\resumeSubHeadingListStart

  \resumeSubheading
  {ICONS Laboratory}{Incheon, Republic of Korea}
  {Undergraduate Researcher (Advisor: Prof. Hyunbum Kim)}{Mar. 2024 -- Present}
  \resumeItemListStart
    \item Investigated network optimization and resource efficiency in UAV-assisted ITS systems
    \item Investigated IoT platform--based decision-making architectures in distributed system environments
  \resumeItemListEnd

  \vspace{0.5em}

  \resumeSubheading
  {Hyundai H-Mobility Class}{Republic of Korea}
  {Autonomous Driving Track (Advanced Communication \& Networking)}{Apr. 2025 -- Jul. 2025}
  \resumeItemListStart
    \item Completed coursework in perception, decision-making, control, and communication.
    \item ROS 2-based autonomous driving training / CAN, LIN, Ethernet, and V2X communication
  \resumeItemListEnd

\resumeSubHeadingListEnd

\section{\textbf{Publications and Presentations}}
\small{
  \begin{enumerate}[itemsep=0.8em]

    \item \textbf{\underline{H. Kim}}, H. Kim, W. Kim, A. V. Vasilakos, and P. Bellavista,
    \textbf{``Resting Drone-Enabled Enhanced ITS Coverage and V2X Integration Network Management for Urban Mobility Service,''}
    \textit{IEEE TNSM}, Mar. 2026.

    \item \textbf{\underline{H. Kim}}, J. Ben-Othman, B. Lee, and H. Kim,
    \textbf{``Split Federated Learning-Enabled Deep Q-Networks for Generalized Path Planning in Distributed IoT Edge Computing,''}
    \textit{IEEE Internet of Things Journal}, Mar. 2026.

    \item \textbf{\underline{H. Kim}}, H. Kim, and M. Guizani,
    \textbf{``A Resting Drone-enabled Surveillance Framework for Real-time \\
    Monitoring with Resource Efficiency in IoT-based Smart Cities,''}
    \textit{IEEE Internet of Things Journal}, Aug. 2025.

    \item \textbf{\underline{H. Kim}} and H. Kim,
    \textbf{``Analysis of Opportunistic Wi-Fi/LTE Connectivity Strategies \\
    for Outdoor Autonomous Driving Platforms in ITS Environments,''}
    Proc. of KICS Fall Conf., Oct. 2025. (Oral)

    \item \textbf{\underline{H. Kim}}, M. Kim, and H. Kim,
    \textbf{``Analysis of V2V Shortest Path Search and Connection Strategies in ITS Environment Using Low-Power Short-Range Communication,''}
    Proc. of KICS Fall Conf., Oct. 2024. (Poster)

  \end{enumerate}
}

\section{\textbf{Projects (Undergraduate)}}
\resumeSubHeadingListStart

\resumeProject
{\href{https://www.youtube.com/watch?v=FVn5UPFTrjI}{RoboCup@Work Mobile Manipulator: Autonomous Pick-and-Place Robot}}
{}
{Jul. 2025 -- Present}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Team Leader, Autonomous Driving Team
  \item \textbf{Tech Stack}: ROS 2, Jetson Orin AGX, Rainbow Robotics RB-3, RH-P12-RN Gripper, Intel RealSense D435
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em]
    \item Autonomous navigation of a mobile manipulator to task-relevant workstations
    \item Vision-assisted pick-and-place manipulation using a 6-DoF robotic arm and parallel gripper
    \item Integrated perception, navigation, and manipulation pipelines for real-world task execution
  \end{itemize}
\resumeItemListEnd

\vspace{0.5em}

\resumeProject
{\href{https://github.com/EliseEgkart/capstone_final_ws}{Capstone Design : Last-Mile Delivery Robot}}
{}
{Nov. 2025 -- Present}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Team Leader
  \item \textbf{Tech Stack}: ROS 2, 2D LiDAR (slamtec), ntel RealSense D435, IMU, Jetson Orin Nano, SLAM, Nav2, Moveit
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em]
    \item Enabled autonomous navigation to designated goal locations using localization results
    \item Estimated odometry using in-wheel motors with encoders and performed Cartographer-based SLAM
    \item Implemented vision-based elevator button recognition and IMU-based floor transition detection
  \end{itemize}
\resumeItemListEnd

\vspace{0.5em}

\resumeProject
{\href{https://github.com/EliseEgkart/iPBL_FPV_car_project}{FPV-Based RC Car Racing}}
{}
{Nov. 2025 -- Dec. 2025}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Team Leader
  \item \textbf{Tech Stack}: ESP32-C3, Arduino, BLE, ESP-NOW, FPV System (Camera \& Goggles), Fusion 360
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em]
    \item Developed FPV-based RC car firmware supporting BLE and ESP-NOW communication
    \item Implemented real-time steering and speed control using joystick-based commands
    \item Designed and fabricated RC car chassis and bumper using Fusion 360 for racing durability
  \end{itemize}
\resumeItemListEnd

\vspace{0.5em}

\resumeProject
{\href{https://github.com/UNITA2025}{Real-World Autonomous Driving Vehicle (ERP-42 Platform)}}
{}
{Apr. 2025 -- Nov. 2025}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Team Leader
  \item \textbf{Tech Stack}: ROS 2, 3D LiDAR (VLP-16), Camera, RTK-GNSS, IMU, Vehicle Control
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em]
    \item Performed navigation driving using sensor fusion of RTK-GNSS and IMU
    \item Developed Pure Pursuit and PID-based vehicle control and onboard communication protocols
    \item Implemented object detection and obstacle avoidance logic using camera and Velodyne VLP-16 sensor fusion
  \end{itemize}
\resumeItemListEnd

\vspace{0.5em}

\resumeProject
{\href{https://github.com/EliseEgkart/ECS_Autonomous_driving_based_on_computer_vision}{Line-Following (CV) Autonomous RC Car}}
{}
{May 2025 -- Jun. 2025}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Course Project
  \item \textbf{Tech Stack}: Raspberry Pi, Arduino, OpenCV, Python, UART/Serial, PID Control
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em]
    \item Built a line-following autonomous RC car using camera-based computer vision for lane detection
    \item Integrated Raspberry Pi image processing with PID steering control and Arduino motor/servo actuation
    \item Implemented dual-mode control enabling manual RC and autonomous driving via UART communication
  \end{itemize}
\resumeItemListEnd

\vspace{0.5em}

\resumeProject
{\href{https://github.com/EliseEgkart/ECS_Interactive_Reactions}{Virtual Gesture Interface Board}}
{}
{Apr. 2025 -- May 2025}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Course Project
  \item \textbf{Tech Stack}: JavaScript, p5.js, ml5.js (HandPose), Webcam, OBS
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em]
    \item Implemented hand gesture recognition using ml5.js HandPose
    \item Developed gesture-based mode switching and interactive on-screen reactions
    \item Integrated drawing palette interactions and streamed output via OBS Virtual Camera
  \end{itemize}
\resumeItemListEnd

\vspace{0.5em}

\resumeProject
{\href{https://www.youtube.com/watch?v=_1o2Oad9vVQ}{Resting Drone}}
{}
{Mar. 2024 -- Nov. 2024}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Team Leader
  \item \textbf{Tech Stack}: Pixhawk 4, PX4 Autopilot, Optical Flow, LiDAR, Servo Motor Control, ECU \& PM Board
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em]
    \item Developed an energy-efficient resting drone that attaches to structures to eliminate hovering
    \item Implemented servo-based attachment maneuvers with optical flow--based attitude stabilization
    \item Built a PX4-based autonomous flight control system using Pixhawk 4
  \end{itemize}
\resumeItemListEnd

\vspace{0.5em}

\resumeProject
{\href{https://youtu.be/RuwLuphqz50}{Automated Tanghulu Manufacturing Machine}}
{}
{Jan. 2024 -- Apr. 2024}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Entrepreneurship Club
  \item \textbf{Tech Stack}: ESP32, OLED Display, DC Motor, Fusion 360
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em]
    \item Developed an OLED-based user interface for motor speed and operation time control
    \item Implemented joystick-based interface control and DC motor speed adjustment
    \item Contributed to filing four related patents (KR 10-2024-0040087 to 10-2024-0040090)
  \end{itemize}
\resumeItemListEnd

\vspace{0.5em}

\resumeProject
{\href{https://moonshotfps1.notion.site/FPS-CONSOLE-PROJECT-1-efc70c403e4e4eee8b17e8ac6a4f5c15?pvs=74}{FPS Gun Console System}}
{}
{Sep. 2023 -- Dec. 2023}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Team Leader
  \item \textbf{Tech Stack}: ESP32, Bluetooth Classic (SPP), Unity, OpenCV, IMU
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em]
    \item Implemented a semi-virtualized IMU-based aiming system aligning muzzle orientation with on-screen view
    \item Enabled real-time input transmission via Bluetooth using ESP32 for PC FPS game integration
    \item Designed a Unity-based input emulation framework compatible with commercial FPS titles
  \end{itemize}
\resumeItemListEnd

\vspace{0.5em}

\resumeProject
{\href{https://www.youtube.com/shorts/RJIRCw1mdC4}{Unity-Based Game Development Project}}
{}
{Jul. 2023 -- Sep. 2023}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Personal Projects
  \item \textbf{Tech Stack}: Unity
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em]
    \item Game Project 1: Bird Flight Simulation Game
    \item Game Project 2: 2D Side-Scrolling Action Platformer
    \item Game Project 3: Top-Down Arena Roguelike Action Game
  \end{itemize}
\resumeItemListEnd

\vspace{0.5em}

\resumeProject
{\href{https://www.youtube.com/watch?v=8pNXA40yGwk}{Wireless Mobile Fan Control System : Fan-Li}}
{}
{Sep. 2021 -- Dec. 2021}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Team Leader
  \item \textbf{Tech Stack}: Arduino, ESP32-CAM, Bluetooth Control App, Real-time Streaming, Fusion 360
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em, topsep=0pt, itemsep=0pt, parsep=0pt]
    \item Enabled wireless control of the fan via a Bluetooth-based mobile app
    \item Implemented real-time video streaming using ESP32-CAM
    \item Integrated mobility and airflow control into a mobile fan system
  \end{itemize}
\resumeItemListEnd

\vspace{0.5em}

\resumeProject
{\href{https://youtube.com/shorts/7Net92QTvlI?feature=share}{Intelligent Book Arrangement Robot (IBA)}}
{}
{May 2021 -- Sep. 2021}
{}
\vspace{-1.5em}
\resumeItemListStart
  \item \textbf{Role}: Team Member
  \item \textbf{Tech Stack}: Arduino, RFID, DC Motor, Servo Motor, Stepper Motor
  \item \textbf{Key Features}:
  \begin{itemize}[leftmargin=1.2em, topsep=0pt, itemsep=0pt, parsep=0pt]
    \item Implemented RFID-based localization using floor-mounted tags
    \item Built a multi-motor control system for navigation and book handling
    \item Supported vision-based book classification for automated sorting
  \end{itemize}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{\textbf{Leadership \& Ambassador Activities}}
\resumeSubHeadingListStart

  \resumeProject
  {Autonomous Driving Track Ambassador, Hyundai H-Mobility Class}
  {Hyundai Motor Group}
  {Apr. 2025 -- Jul. 2025}
  {}
  \resumeItemListStart
    \item Selected as an Autonomous Driving Track ambassador and produced \\weekly educational summary content and promotional materials for the program.
  \resumeItemListEnd

  \vspace{0.5em}

  \resumeProject
  {President, UNITA Robotics \& Mobility Club (3rd Cohort)}
  {Incheon National University}
  {Jan. 2026 -- Present}
  {}
  \resumeItemListStart
    \item Designed, lectured, and led a ROS 2-based autonomous robotics curriculum, \\incorporating quizzes, student presentations, and hands-on projects.
  \resumeItemListEnd

  \vspace{0.5em}

  \resumeProject
  {President, UNITA Robotics \& Mobility Club (2nd Cohort)}
  {Incheon National University}
  {Apr. 2025 -- Dec. 2025}
  {}
  \resumeItemListStart
    \item Led an autonomous mobility competition team and developed a sensor fusion--based \\autonomous driving system using 3D LiDAR, cameras, GNSS-RTK and IMU
  \resumeItemListEnd

\resumeSubHeadingListEnd

\section{\textbf{Technical Skills (Core Tools I Use Daily)}}
\begin{center}
\small
ROS 2 \,|\, C/C++ \,|\, Python \,|\, Arduino (Platform) \,|\, Linux (Ubuntu) \,|\, Git/GitHub \,|\, Markdown \,|\, LaTeX
\end{center}

\section{\textbf{Awards}}
\resumeSubHeadingListStart

  \resumeProject
  {Outstanding Learner Award, Hyundai H-Mobility Class}
  {Hyundai Motor Group R\&D Division Head Award}
  {Jul. 2025}
  {}
  \vspace{0.3em}

  \resumeProject
  {Grand Prize, Department of Embedded Systems Engineering Graduation Project Competition}
  {College of Information Technology Dean's Award, Incheon National University}
  {Jun. 2026}
  {Role: Team leader}
  \vspace{0.3em}

  \resumeProject
  {Grand Prize, Self-Built Electric Vehicle Competition}
  {Future Automotive Convergence Innovation Center Director Award, Incheon National University}
  {Dec. 2025}
  {Role: Team leader}
  \vspace{0.3em}

  \resumeProject
  {Special Prize, National Creative Capstone Design Competition}
  {Korea Technopark Promotion Association President Award}
  {Nov. 2024}
  {Role: Team leader}
  \vspace{0.3em}

  \resumeProject
  {Bronze Prize, Sungkyunkwan University Consortium Creative Capstone Design Competition}
  {Engineering Education Innovation Center Director Award, Sungkyunkwan University}
  {Nov. 2024}
  {Role: Team leader}
  \vspace{0.3em}

  \resumeProject
  {Grand Prize, Incheon National University Creative Capstone Design Competition}
  {Incheon National University President Award}
  {Sep. 2024}
  {Role: Team leader}
  \vspace{0.3em}

  \resumeProject
  {Grand Prize, Software Contest of the College of Information Technology}
  {College of Information Technology Dean's Award, Incheon National University}
  {Dec. 2023}
  {Role: Team leader}
  \vspace{0.3em}

  \resumeProject
  {Grand Prize, INU Maker Competition}
  {Incheon National University President Award}
  {Jan. 2022}
  {Role: Team leader}
  \vspace{0.3em}

  \resumeProject
  {Honorable Mention, Smart Mobility Competition}
  {Engineering Education Innovation Center Director Award, Incheon National University}
  {Dec. 2021}
  {Role: Team leader}
  \vspace{0.3em}

  \resumeProject
  {Bronze Prize, INU Autonomous Driving Software Competition}
  {College of Information Technology Dean's Award, Incheon National University}
  {Nov. 2021}
  {Role: Team member}
  \vspace{0.3em}

\resumeSubHeadingListEnd

\section{\textbf{Teaching Experience}}
\resumeSubHeadingListStart
  \resumeProject
  {Teaching Assistant, Matrix}
  {Department of Embedded Systems Engineering, Incheon National University}
  {Spring 2025; Fall 2025}
  {Undergraduate course}
  \vspace{0.3em}
\resumeSubHeadingListEnd

\end{document}
